---
title: "Linear_regression_on_salary_data"
output: html_document
---

### In this Task we can predict the salary data on the basis their experice what they actually get and we can predict the salary data on the basis of the dataset.

## Firstly, we Load the data on the variable, as we see ww have a dataset in xlsx format so we add library "readxl" is used for excel data.

```{r setup, include=FALSE}

library(readxl)

salary_Data <- read_excel("Salary_Data.xlsx")

```

## we check the dataset

```{r cars}

par(mfrow = c(1,2))
head(salary_Data)
summary(salary_Data)
```

## we start EDA process on the data EDA Stands for "Explorartory Data Analysis" and it is also known as "Pre processing"

# 1. Variable identification
# 2. Univariate analysis
# 3. Bivariate analysis
# 4. Missing Value Treatment
# 5. Outlier Treatment
# 6. varible transformation
# 7. variable creation

# but as we see we do not have any outlier no any missing values and no need to ananlysis (univariate and bivariate) becouase we have a small two column dataset.
# but else we can check outlier with the graph 



```{r pressure, echo=FALSE}

par(mfrow = c(1,2))
boxplot(salary_Data$YearsExperience, main = "Experience in years")
boxplot(salary_Data$Salary,  main = "Salary")

```
## library "caTools" helps to break the dataset because we need to break the dataset in two dataset test and train.

#  training dataset and test dataset

# sample.split works for only target variable and splitratio convert part you want to take for training

```{r}

library(caTools)

set.seed(10)

split_salary_data <- sample.split(salary_Data$Salary, SplitRatio = 0.75)

split_salary_data



```


## as we see we have a split data in form of True and False so we have to compaew True for  training and Fase for Test


```{r}
train = subset(salary_Data, split_salary_data == T)

testdata = subset(salary_Data, split_salary_data == F)

head(train)
head(testdata)

```

## creating the model on training Data

```{r}

model <- lm(formula = Salary~., data = train)

summary(model)

```
## predict the model with the test data

```{r}


prediction <- predict(model, testdata)

prediction



```

## So, we can add these data on the test dataframe and we the difference its easy to say model is corrrect or not

# we can use cbind for the combine the columns in the test dataset

```{r}
difference <- (testdata$Salary - prediction)
testdata <- cbind(testdata, prediction, difference)

testdata
```
## In the difference columns shows we can ignore 11% error and our model is prediction is good 

## we also find mean absolute percentage error or deviation (MAPE or MAPD)

```{r}

mape <- mean(abs(difference)/ testdata$Salary)
mape
```

## as we see our map is very low 3% . So the prediction is enough to say more experience have more salary. 






























